Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$

### 2015-05-08 formalwriteup.tex
revisions to intro + ci argument

\begin{abstract}
We study the polynomial representation of the ratioal Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$. We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient. Our methods are motivated by generalizing from characteristic $0$ to characteristic $p$. \end{abstract}

@@

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$. This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$). In general new techniques are required to study positive characteristc as opposed to characteristic 0. In this paper we directly connect the characteristc 0 case to the positive characteristic case; instead of taking complex residues, we consider the coefficients of formal power series in positive characteristic. While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions

@@

We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.

@@

\begin{proof}
%Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations. We see that this means we can apply the Dunkl operators to $F_a$ and check that the coefficient of $z^p$ in the result is $0$ to show that the Dunkl operators annihilate the $f_a$.
%
%We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$. Therefore we need only consider the action of the Dunkl operators on $F_0$. We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators. 
%
%We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$. In particular, we note that since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$, we have $z^2 \mid g-1$. Then since $p>2$, we note that $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$. Therefore we can add multiples of $(g-1)^{p-1}$ when taking the Dunkl operator's action on $F_0$, since even when multipled by another power series it cannot contribute anything to the coefficient of $z^p$. We also note that we can add $n$ times any multiple of $F_0$ since $n \equiv 0 \bmod p$.

@@

\begin{align*}
\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
\end{align*}
%
%\begin{align*}
%&=V_i\frac{\partial}{\partial x_i}\left(\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{i}^kz^k\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} -k\binom{c}{k}(-1)^kx_{n-1}^{k-1}z^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-1} k\binom{c}{k}(-1)^kx_{i}^{k-1}z^k\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{n-1}^{k-1}z^k\right)-V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{i}^{k-1}z^k\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)(1-x_{n-1}z)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)(1-x_iz)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{n-1}^{k+1}z^{k+2}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{i}^{k+1}z^{k+2}\right)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}+ \sum_{k=0}^{p-1}c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
%\end{align*}
%\begin{align*}
%&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F+\\&\;\;\;\;\;V_i\frac{1}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(- c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p}\right)-\\&\;\;\;\;\;V_i\frac{1}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( -c\binom{c-1}{p-1}(-1)^{p-1}x_{i}^{p-1}z^{p}\right)\\
%\end{align*}
%
%Let $G_i=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$. Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.

We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$

@@

\begin{align*}
\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}

%\begin{align*}
%\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\prod_{i=0}^{n-1} \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\\
%&=\sum_{i=0}^{n-1}\left(\left(\sum_{k=1}^{p-1} k\binom{c}{k}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left((1-x_iz)\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^kx_i^kz^{k-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(\sum_{k=1}^{p-1} c\binom{c-1}{k-1}(-1)^{k+1}x_i^{k+1}z^{k}+\sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k+1}x_i^{k+1}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}+\sum_{k=0}^{p-1} -cx_i\binom{c}{k}(-1)^{k}x_i^{k}z^{k}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\right)\\
%&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F+\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)\\
%\end{align*}
%
%Let $V=\sum_{i=0}^{n-1}\frac{1}{1-x_iz}\left(-c\binom{c-1}{p-1}(-1)^px_i^pz^{p-1}\right)\prod_{j \ne i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_j^kz^k\right)$. Then $\frac{\partial F}{\partial z}=V+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F$. 
%

We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$

@@

We consider $V(z),G_1(z),G_0(z)$; since $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$ and $(g-1)^{p-1}$ divides $V(z),G_1(z),G_0(z)$, we see that for $0 \le \ell \le p$ that $$[z^\ell]V(z)=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.$$

@@

%
%Since $c$ is generic, we can write the $f_a$ as polynomials in $c$ with coefficients from the polynomial ring $A$; we can therefore consider the `constant term' of $f_a$ as a polynomial in $c$. Recall that $f_a$ is the coefficient of $z^p$ in $F_a=\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. Then as polynomials it is clear that $c \mid \binom{c}{k}$ for all $k > 0$; therefore when trying to find the constant term of the coefficient of $z^p$, we can ignore the terms with $k > 0$ in the second multiplicand. The term for $k=0$ is just $1$; it is then clear that the constant term (the coefficient of $c^0$) of $f_a$ is $x_a^p$.
%
%If $\sum_{a=0}^{n-2} \lambda_af_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$. We assume that not all of the $\lambda_a$ are $0$. Then we can let $e$ be the smallest nonnegative integer such that there exists an index $b$ with the coefficient of $c^e$ in $\lambda_b$ nonzero. We can divide all of the $\lambda_a$ by $c^e$, so that $\lambda_b$ for some $b$ must have nonzero constant term.
%
%The constant term of the sum is $\sum_{a=0}^{n-2}\mu_ax_a^p$ where $\mu_a$ is the constant term of $\lambda_a$. Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $\mu_a$ must be $0$ for $a=0,\dots,n-2$ . Then in particular the constant term $\mu_b$ of $\lambda_b$ is $0$, a contradiction. This means that our assumption that not all of the $\lambda_a$ were $0$ is false, so $\lambda_a=0$ for all $a$. 
%
%Then since $\sum_{a=0}^{n-2} \lambda_af_a=0$ means all the $\lambda_a$ are $0$, we see that $f_a$ for $a=0,\dots,n-2$ are linearly independent as desired.

@@

This implies that the product of the Vandermonde matrix $$\left(\begin{smallmatrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{smallmatrix}\right)$$ with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.

@@

@@

The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-l-r$. We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$. Therefore we have a linear dependence relation between $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$ - we can assume this is nonzero since $c$ is generic and none of the $y_i$ are $0$. Therefore we can write $[z^\ell]a(z)$ as a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$.

@@

We can assume without loss of generality that $y_{r-1}=0$. Then if $r>1$, we can go through the same argument again with $y_0,\dots,y_{r-2}$ and find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct. Therefore we must have $r=1$ and $y_0=0$.

%We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $K$. Then we can consider $f_a$ as a function on these vectors $x$ for all $a$. For any rational function $u( c)$, we let $u(c )x=\langle u(c )x_0,\dots, u(c )x_{n-2}\rangle$. 
%
%To show that $A/I$ is a complete intersection, we will show that if $f_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$, which is an equivalent condition. 
%
%By Proposition~\ref{prop:linind}, $f_a$ is a homogeneous polynomial in the $x_i$ of degree $p$ for all $a$. Then for any rational function $u(c )$, we see that $f_a(u(c )x)=u(c )^pf_a(x)$. In particular, if $f_a(x)=0$, then for any rational function $u(c )$ we have $f_a(u(c )x)=0$ as well. Therefore if $f_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial in $c$ for all $i=0,\dots,n-2$ (a least common denominator), we see that since $f_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$. We assume that not all of the $x_a$ are $0$. Then we can find the smallest nonnegative integer $e$ such that there exists an $b$ with the coefficient of $c^e$ in $x_b$ nonzero. Then since $f_a(\frac{1}{c^e}x)=0$ and $x_i/c^e$ is still a polynomial for any $i$, we see that we can assume that the constant term of $x_b$ for some $b$ is nonzero by dividing through by $c^e$. 
%
%For any $a$, we can then consider $f_a(x)$ to be a polynomial in $c$. Since this is zero, we can in particular consider the constant term, which must be $0$. The constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power. If this is zero, then the constant term of $x_a$ must be $0$. 
%
%Then if $f_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$. In particular, $x_b$ has zero constant term, a contradiction. This means that our assumption that not all of the $x_a$ were $0$ is false, so $x_a=0$ for all $a$. 
%
%Therefore $f_0(x) = \dots = f_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection.
\end{proof}

>>>>

\begin{abstract}
We study the polynomial representation of the rational Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$. We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient. Our methods are motivated by generalizing from characteristic $0$ to characteristic $p$. \end{abstract}

@@

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$. This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$). In general new techniques are required to study positive characteristic as opposed to characteristic 0. In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues. In the positive characteristic case, we instead let the generators be the coefficients of formal power series. In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic. We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $\Sigma_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.

While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions

@@

%We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.

@@

@@

\begin{align*}
\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
\end{align*}
We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$

@@

\begin{align*}
\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$

@@

We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$. We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$. Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$. Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$. (We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)

Then we see that for $0 \le \ell \le p$ we have $$[z^\ell](z^2V(z))=[z^\ell]G_0(z)=[z^\ell]G_1(z)=0.$$

@@

@@

This implies that the product of the Vandermonde matrix $$\left(\begin{matrix} 1& 1& \dots& 1\\y_0&y_1&\dots&y_{r-1}\\\dots&\dots&\dots&\dots\\y_0^{r-1}&y_1^{r-1}&\dots&y_{r-1}^{r-1}\end{matrix}\right)$$ with the column vector $(\lambda_0,\dots,\lambda_{r-1})$ is $0$; however since all the $y_i$ are distinct, the Vandermonde matrix has nonzero determinant $\prod_{0 \le i < j \le r-1} (y_i-y_j)$, implying that $\lambda_i=0$ for all $i$.

@@

We will show that we must have $[z^0]a(z)=0$, a contradiction. Note that if $r > p$ then we have already shown that; therefore we assume $r \le p$.

@@

The lowest degree term of the formal power series $z^ph_\ell(z)b(z)$ has degree at least $p-\ell-r$. We note that we must have $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$.

Then as long as $p-\ell-r \ge 0$, which is true when $\ell \le p-r$, we see that $[z^{-1}]\left(\frac{d}{dz}( h_\ell(z) a(z))\right)=0$ is a linear combination of $[z^\ell]a(z),[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ in which $[z^\ell]a(z)$ has nonzero coefficient $ (-1)^r  \prod_i y_i\left((\ell + r) - \sum_i m_i c\right)$ - we can assume this is nonzero since $c$ is generic and none of the $y_i$ are $0$. Therefore we can write $[z^\ell]a(z)$ as a linear combination of $[z^{\ell+1}]a(z),\dots,[z^{\ell+r}]a(z)$ when $\ell \le p-r$.

@@

We can assume without loss of generality that $y_{r-1}=0$. Then if $r>1$, we can go through the same argument again with $y_0,\dots,y_{r-2}$. We are able to do this because our calculation of $F'(z)$ and $V(z)$ so that $z^p \mid V(z)$ relies only on the fact that $\sum m_iy_i=0$, which will still be true if we leave out $y_{r-1}=0$. We will then find that one of the $y_i$ with $i < r-1$ is $0$, which gives a contradiction since the $y_i$ are distinct. Therefore we must have $r=1$ and $y_0=0$.
